---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Harmonizome

<!-- badges: start -->

<!-- badges: end -->

The goal of Harmonizome is to provide a fast interface to download and perform functional and gene set enrichment analysis.

## Installation

You can install the development version of Harmonizome from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marceelrf/Harmonizome")
```

## Example

```{r,echo=FALSE}
for (f in list.files(full.names = T,pattern="*.R",path = "R/")) {
    source(f)
}
for (f in list.files(full.names = T,pattern="*.rda",path = "data/")) {
    load(f)
}
```

The function `show_dataset_collection` is used to check all available datasets.

```{r}
show_dataset_collection()
```

Let's use the [*SILAC Phosphoproteomics Signatures of Differentially Phosphorylated Proteins for Drugs* dataset](https://maayanlab.cloud/Harmonizome/dataset/SILAC+Phosphoproteomics+Signatures+of+Differentially+Phosphorylated+Proteins+for+Drugs) using the code **silacdrug** in the function `get_geneset`.

**CAUTION**: Depending on the size of your data set and your internet connection this step could take a long time!!!

```{r}
silacdrug_ds <- get_geneset(code = "silacdrug")
```

```{r}
head(silacdrug_ds)
```
